Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-08-20 mu/article/prb/article.tex
Including all necesary to send the article to PRB

%\documentclass[prb,11pt,tightenlines,twocolumn,aps]{revtex4-1}
\documentclass[floatfix,prb,aps,superscriptaddress,showpacs,11pt,preprint,letterpaper]{revtex4}
%\documentclass[preprint,prb,showpacs]{revtex4}
\usepackage{amsmath}    % need for subequations 
\usepackage{graphicx}   % need for figures 
\usepackage{verbatim}   % useful for program listings 
\usepackage{color}      % use if color is used in text 
\usepackage{subfigure}  % use for side-by-side figures 
\usepackage[pdffitwindow,colorlinks,citecolor={red},linkcolor={blue}]{hyperref}
\usepackage[dvipsnames]{xcolor}
\usepackage{multirow}
\usepackage{soul}
%\usepackage[inline]{showlabels}
% \input{/Users/bms/util/definitions}
%\input{/Users/reinaldo/Documents/tex_files/bmsdefinitions.tex}
\def\tama{10cm}
\raggedbottom           % don't add extra vertical space

@@

\begin{abstract}
We present a theoretical study of spin-velocity injection (SVI) of a pure spin
current (PSC) induced by  a linearly polarized light that impinges normally on
the surface of  two 50\% hydrogenated noncentrosymmetric two-dimensional 2D
graphene structures. The first structure, hydrogenated at only one side,
labeled Up, also known as graphone, and the second, labelled Alt, is
25\% hydrogenated at both sides. The hydrogenation opens an energy gap in both
structures. We analyze two possibilities: in the first, the spin is fixed
along a chosen direction, and the resulting SVI is calculated.
In the second, we choose the SVI direction along
the surface plane, and calculate the resulting
spin orientation. This is done by changing the energy
$\hbar\omega$ and polarization angle $\alpha$  of the incoming  light. The
results are calculated within a full electronic band structure scheme using the
Density Functional Theory (DFT) in the Local Density Approximation (LDA). The
maxima of the spin-velocities are reached when $\hbar\omega=0.084$\,eV and
$\alpha=35^\circ$ for the Up structure, and $\hbar\omega=0.720$\,eV and
$\alpha=150^\circ$ for the Alt geometry. We find a speed of 668\,Km/s and
645\,Km/s for the Up and the Alt structures, respectively, when the spin points
perpendicularly to the surface. Also, the response is maximized by
fixing the spin-velocity direction 
along a high symmetry  axis, obtaining a speed of 688Km/s
with the spin pointing at $13^\circ$ from the surface normal, for the Up, 
and 906 Km/s and the spin pointing at $60^\circ$ from the surface normal, for
the Alt system. These speed values are  of order of magnitude larger than those of bulk semiconductors,
such as CdSe and GaAs, thus making the hydrogenated graphene structures
excellent candidates for spintronics applications. 
\end{abstract}

@@

Both the Up and the Alt  structures
are noncentrosymmetric, and therefore,
they are good candidates in which SVI can be
induced. In this article, 
we address theoretically the spin-velocity injection
by one-photon absorption of linearly polarized light, analyzing
in our structures,
two possible scenarios of practical interest. 
The first case is by fixing the spin of the electrons along $z$, i.e. 
perpendicular 
to the surface plane, with the resulting velocity
directed along the surface of the
structures in the $xy$ plane. 
In the second case we fix the SVI velocity along the
$x$ or $y$ direction, and then, the resulting spin is directed outward of the
$xy$ plane.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=5cm]{fig1}
    \caption{(color online) Top (top panel) and side (bottom panel) views of
the Up structure along with the Cartesian $x$, $y$, and $z$ directions. The
dark (light) spheres are the C (H) atoms. The primitive hexagonal unit cell is
also shown.}
    \label{fig:up-struc}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=5cm]{fig2}
    \caption{(color online) Top (top panel) and side (bottom panel) views of
the Alt structure along with the Cartesian $x$, $y$, and$ z$ directions. The
dark (light) spheres are the C (H) atoms. The primitive rectangular unit cell
is also shown. }
    \label{fig:alt-struc}
\end{figure}

@@

We calculated the self-consistent ground state and the Kohn-Sham states within
density functional theory in the local density approximation (DFT-LDA), with a
planewave basis using the ABINIT code \cite{gonzeCPC09}. We used Hartwigsen-
Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
pseudopotentials \cite{hartwigsenPRB98}, including the spin-orbit interaction
needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ from Eq.
\eqref{eq:mu}.
The convergence parameters for the calculations,  corresponding to the Up and
Alt structures are cutoff energies up to 65\,Ha, resulting in LDA
energy band gaps of 0.084\,eV and 0.718\,eV, respectively, 
and 14452 ${\mathbf k}$ points in the IBZ
where the energy
eigenvalues and matrix elements were calculated;
to
integrate $\mu^{\mathrm{abcd}}(\omega)$ and
$\xi^{\mathrm{a}\mathrm{b}}(\omega)$ the linearized analytic tetrahedron method
(LATM) has been used.\cite{nastosPRB07} 
We neglect the anomalous velocity term
$\hbar(\boldsymbol{\sigma}\times\nabla V)/4m^2c^2$, where $V$ is the crystal
potential, in $\hat{\mathbf v}$ of Eq.~\eqref{z.1}, as this term is known to
give small contribution to PSC.\cite{bhatPRL05} Therefore, $[\hat{\mathbf
v},\hat{\mathbf S}]=0$, and Eq.~\eqref{z.1} reduces to $\hat
K^{\mathrm{a}\mathrm{b}}=\hat v^\mathrm{a} \hat S^\mathrm{b}=\hat S^\mathrm{b}
\hat v^\mathrm{a}$. Finally, the prime in the sum of Eq.~\eqref{eq:mu} is
restricted to quasi-degenerated conduction bands $c$ and $c'$ that are closer
than 30 meV to each other, which  is both typical laser- pulse energy width and the thermal
room-temperature energy level broadening.\cite{nastosPRB07}

@@

In the top panel of Fig. \ref{fig:up-vsz-w1}, we plot
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ {\it vs.}
0.080\,eV$\leq\hbar\omega\leq$0.096\,eV (similar energy range for the Up
structure shown in the left panel of Fig.~\ref{fig:vab-str-comp}) and
$0^\circ\leq\alpha\leq 180^\circ$. We see a broad peak that reaches the maximum
of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 739.7$\,Km/s at
$\alpha=35^{\circ}$ and $\hbar\omega= 0.084$\,eV.  The variation of
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ as a function of $\alpha$,
which comes from the interplay of the $\boldsymbol{\mu}$ tensor components as
multiplied by the  trigonometric functions of Eq.~\eqref{eq:vab-aw}, gives a
sizable set of values between 739.7\,Km/s and 165.4\,Km/s, for
0.084\,eV$\leq\hbar\omega\leq$0.090\,eV. In the bottom panel, we show
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ {\it vs.} $\alpha$ (left scale,
black solid line), at $\hbar\omega= 0.084$\,eV, thus following the ridge in the 3D
plot of the top panel. Also, we plot the corresponding velocity angle
$\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red
short-dashed line), where it
is very interesting to see that $\gamma_{\sigma^z}(\omega,\alpha)$ is centered
at 64.55$^\circ$ with a rather small deviation of only $\pm 0.03^\circ$, for
the whole range of $\alpha$. This result means that for $\hbar\omega=0.084$ eV
and for all values of $\alpha$, the electrons, with the chosen spin pointing
along $z$, will move at the angle of $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)
\sim 64.5^{\circ}$ with respect to the $x$ direction, with the range of  high
speeds $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ shown in the figure.
Also, from Eq. \eqref{eq:gamma-par} we find that
$\gamma^\parallel_{\sigma^\mathrm{z}} (\omega,\alpha)=\alpha = 64.56^\circ$,
with $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 631.1$\,Km/s 
(as indicated by the green dot-dashed arrow), and that from Eq. \eqref{eq:gamma-perp},
$\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=64.50^\circ$,
gives $\alpha=154.50^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 191.5$ Km/s 
(as indicated by the orange long-dashed 
arrow). 
Thus, at $\hbar\omega=0.084$ eV, an incident field, polarized at
$\alpha \sim 65.5^\circ$ or $\sim 154.5^\circ$, injects electrons with their
spin polarized along $z$, which move parallel or perpendicular to the incident
electric field,  with a speed of 631.14\,Km/s or 191.5\,Km/s, respectively.

Now, we analyze the results for the second energy range of the Up structure
shown in Fig.~\ref{fig:vab-str-comp}. In the top panel
of Fig. \ref{fig:up-vsz-w2}, we plot $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha)$ {\it vs.} 1.950\,eV$\leq\hbar\omega\leq$1.960\,eV and
$0^\circ\leq\alpha\leq 180^\circ$. We see two broad peaks that maximize at
$\alpha=35^{\circ}$ and $\hbar\omega= 1.954$\,eV, with a value of
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 193.5$\,Km/s, and at
$\alpha=35^{\circ}$ and $\hbar\omega= 1.957$\,eV, with a value of
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 170.6$\,Km/s. We only
analyze the highest  maximum in the bottom panel, where we  show
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ {\it vs.} $\alpha$ (left scale,
black solid line), at $\hbar\omega= 1.954$\,eV, thus following the highest ridge
shown in the 3D plot of the top panel. Also, we plot the corresponding velocity
angle $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red short-dashed  line),
where in this case we see that the values of $\gamma_{\sigma^z}(\omega,\alpha)$
have more dispersion, as a function of $\alpha$, than for the lower energy
range shown in the bottom panel of Fig.~\ref{fig:up-vsz-w1}. However,
$\gamma_{\sigma^z}(\omega,\alpha)\sim 77.8^\circ$ is nearly constant from
$\alpha=0^\circ$ up to $\alpha\sim 85^\circ$. In this case, we find that
$\gamma^\parallel_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha=78.0^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 115.0$\,Km/s 
(as indicated by the green dot-dashed arrow), and that from Eq. \eqref{eq:gamma-perp},
$\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=167.8^\circ$,
gives $\alpha=77.8^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 65.6$\,Km/s 
(as indicated by the orange long-dashed  arrow). 
Thus, through the correct choice of $\hbar\omega$ and $\alpha$ we could
inject electrons, in this case with their spin polarized along $z$, which move
parallel or perpendicular to the incident electric field, with sizable speeds.

@@

We proceed to analyze the Alt structure, just as we did with the Up structure,
but in this case, we only choose the lower energy range shown in the left
central panel of Fig.~\ref{fig:vab-str-comp}. In the top panel of Fig. 
\ref{fig:alt-vsz}, we plot $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$
{\it vs.} 0.715\,eV$\leq\hbar\omega\leq$0.725\,eV and $0^\circ\leq\alpha\leq
180^\circ$. We see a broad peak that maximizes at $\alpha=150^{\circ}$ and
$\hbar\omega= 0.720$\,eV, with a value of
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 644.9$\,Km/s. In the bottom
panel, we  show $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ {\it vs.}
$\alpha$ (left scale, black solid line), at $\hbar\omega= 0.720$\,eV, thus following
the highest ridge shown in the 3D plot of the top panel. Also, we plot the
corresponding velocity angle $\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$
(right scale, red short-dashed  line), where now we see that
$\gamma_{\sigma^z}(\omega,\alpha)$ is centered at $109.2^{\circ}$ having
variations of $\pm 1.0^{\circ}$ for $0^{\circ} \leq
\alpha \leq 180^{\circ}$. In this case, we find that
$\gamma^\parallel_{\sigma^\mathrm{z}} (\omega,\alpha) =
\alpha = 108.8^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)
= 450.05$\,Km/s (as indicated by the  green dot-dashed arrow), 
and that from Eq. \eqref{eq:gamma-perp},
$\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=110.0^\circ$,
gives $\alpha=20.0^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha) = 60.84$\,Km/s 
(as indicated by the orange long-dashed  arrow). Thus, as for the Up structure,
we could inject electrons with a fixed spin, which moves parallel or
perpendicular to the incident electric field.
% Again, for the cases in which the spin polarization is parallel to the
% surface the maximum values are
% $\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha) = 297.8$ Km/s and
% $\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha) = 606.4$ Km/s,
% corresponding to $\gamma_{\mathrm{x}}(\omega,\alpha) = 116.3^{\circ}$
% $\gamma_{\mathrm{y}}(\omega,\alpha) = 110.1^{\circ}$ and both for
% $\alpha=150^{\circ}$, where the plots are not presented.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\tama]{fig7}
\caption{(color online) For the Up structure we show the velocity
$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black solid line), the polar
angle $\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red dashed  line), and  the
azimuthal angle $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue dot-dashed 
line), {\it vs.} $\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ and
$\mathrm{a}=y$.}
\label{fig:up-vab-comp-rtp-1}
\end{figure}

@@

%@article{buonocorePE16,
%  title={Effects of the substrate on graphone magnetism: A density functional
%  theory study},
%  author={Buonocore, F. and Conte, A. M. and Lisi, N.},
%  journal={Phys. E: Low-dim. Sys.},
%  volume={78},
%  pages={65--72},
%  year={2016},
%  publisher={Elsevier}
%}

gmitraPRL13

>>>>

%\documentclass[prb,11pt,tightenlines,twocolumn,aps]{revtex4-1}
\documentclass[floatfix,prb,aps,superscriptaddress,showpacs,11pt,preprint,letterpaper]{revtex4}
%\documentclass[preprint,prb,showpacs]{revtex4}
\usepackage{amsmath}    % need for subequations 
\usepackage{graphicx}   % need for figures 
\usepackage{verbatim}   % useful for program listings 
\usepackage{color}      % use if color is used in text 
\usepackage{subfigure}  % use for side-by-side figures 
\usepackage[pdffitwindow,colorlinks,citecolor={red},linkcolor={blue}]{hyperref}
\usepackage[dvipsnames]{xcolor}
\usepackage{multirow}
\usepackage{soul}
\def\tama{10cm}
\raggedbottom           % don't add extra vertical space

@@

\begin{abstract}
We present a theoretical study of spin-velocity injection (SVI) of a pure spin
current (PSC) induced by  a linearly polarized light that impinges normally on
the surface of  two 50\% hydrogenated noncentrosymmetric two-dimensional (2D)
graphene structures. The first structure, hydrogenated at only one side,
labeled Up, also known as graphone, and the second, labelled Alt, is
25\% hydrogenated at both sides. The hydrogenation opens an energy gap in both
structures. We analyze two possibilities: in the first, the spin is fixed
along a chosen direction, and the resulting SVI is calculated;
in the second, we choose the SVI direction along
the surface plane, and calculate the resulting
spin orientation. This is done by changing the energy
$\hbar\omega$ and polarization angle $\alpha$  of the incoming  light. The
results are calculated within a full electronic band structure scheme using the
Density Functional Theory (DFT) in the Local Density Approximation (LDA). The
maxima of the spin-velocities are reached when $\hbar\omega=0.084$\,eV and
$\alpha=35^\circ$ for the Up structure, and $\hbar\omega=0.720$\,eV and
$\alpha=150^\circ$ for the Alt geometry. We find a speed of 668\,Km/s and
645\,Km/s for the Up and the Alt structures, respectively, when the spin points
perpendicularly to the surface. Also, the response is maximized by
fixing the spin-velocity direction 
along a high symmetry  axis, obtaining a speed of 688Km/s
with the spin pointing at $13^\circ$ from the surface normal, for the Up, 
and 906 Km/s and the spin pointing at $60^\circ$ from the surface normal, for
the Alt system. These speed values are of order of magnitude larger than those of bulk semiconductors,
such as CdSe and GaAs, thus making the hydrogenated graphene structures
excellent candidates for spintronics applications. 
\end{abstract}

@@

Both the Up and the Alt  structures
are noncentrosymmetric, and therefore,
they are good candidates in which SVI can be
induced. In this article, 
we address theoretically the spin-velocity injection
by one-photon absorption of linearly polarized light, analyzing
in our structures,
two possible scenarios of practical interest. 
The first case is by fixing the spin of the electrons along $z$, i.e.,
perpendicular 
to the surface plane, with the resulting velocity
directed along the surface of the
structures on the $xy$ plane. 
In the second case we fix the SVI velocity along the
$x$ or $y$ direction, and then, the resulting spin is directed outward of the
$xy$ plane.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=5cm]{fig1}
    \caption{(color online) Top (top panel) and side (bottom panel) views of
the Up structure along with the Cartesian $x$, $y$, and $z$ directions. The
dark (light) spheres are the C (H) atoms. The primitive hexagonal unit cell is
also shown.}
    \label{fig:up-struc}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=5cm]{fig2}
    \caption{(color online) Top (top panel) and side (bottom panel) views of
the Alt structure along with the Cartesian $x$, $y$, and $-z$ directions. The
dark (light) spheres are the C (H) atoms. The primitive rectangular unit cell
is also shown. }
    \label{fig:alt-struc}
\end{figure}

@@

We calculated the self-consistent ground state and the Kohn-Sham states within
density functional theory in the local density approximation (DFT-LDA), with a
planewave basis using the ABINIT code \cite{gonzeCPC09}. We used 
Hartwigsen-Goedecker-Hutter (HGH) relativistic separable dual-space Gaussian
pseudopotentials \cite{hartwigsenPRB98}, including the spin-orbit interaction
needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ from Eq.
\eqref{eq:mu}.
The convergence parameters for the calculations,  corresponding to the Up and
Alt structures are cutoff energies up to 65\,Ha, resulting in LDA
energy band gaps of 0.084\,eV and 0.718\,eV, respectively, 
and 14452 ${\mathbf k}$ points in the IBZ
where the energy
eigenvalues and matrix elements were calculated;
to
integrate $\mu^{\mathrm{abcd}}(\omega)$ and
$\xi^{\mathrm{a}\mathrm{b}}(\omega)$ the linearized analytic tetrahedron method
(LATM) has been used.\cite{nastosPRB07} 
We neglect the anomalous velocity term
$\hbar(\boldsymbol{\sigma}\times\nabla V)/4m^2c^2$, where $V$ is the crystal
potential, in $\hat{\mathbf v}$ of Eq.~\eqref{z.1}, as this term is known to
give small contribution to PSC.\cite{bhatPRL05} Therefore, $[\hat{\mathbf
v},\hat{\mathbf S}]=0$, and Eq.~\eqref{z.1} reduces to $\hat
K^{\mathrm{a}\mathrm{b}}=\hat v^\mathrm{a} \hat S^\mathrm{b}=\hat S^\mathrm{b}
\hat v^\mathrm{a}$. Finally, the prime in the sum of Eq.~\eqref{eq:mu} is
restricted to quasi-degenerated conduction bands $c$ and $c'$ that are closer
than 30 meV to each other, which  is both typical laser pulse energy width and the thermal
room-temperature energy level broadening.\cite{nastosPRB07}

@@

In the top panel of Fig. \ref{fig:up-vsz-w1}, we plot
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ {\it vs.}
0.080\,eV$\leq\hbar\omega\leq$0.096\,eV (similar energy range for the Up
structure shown in the left panel of Fig.~\ref{fig:vab-str-comp}) and
$0^\circ\leq\alpha\leq 180^\circ$. We see a broad peak that reaches the maximum
of $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 739.7$\,Km/s at
$\alpha=35^{\circ}$ and $\hbar\omega= 0.084$\,eV.  The variation of
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ as a function of $\alpha$,
which comes from the interplay of the $\boldsymbol{\mu}$ tensor components as
multiplied by the  trigonometric functions of Eq.~\eqref{eq:vab-aw}, gives a
sizable set of values between 739.7\,Km/s and 165.4\,Km/s, for
0.084\,eV$\leq\hbar\omega\leq$0.090\,eV. In the bottom panel, we show
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ (left scale,
black solid line) {\it vs.} $\alpha$, at $\hbar\omega= 0.084$\,eV, thus following the ridge in the 3D
plot of the top panel. Also, we plot the corresponding velocity angle
$\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red
short-dashed line), where it
is very interesting to see that $\gamma_{\sigma^z}(\omega,\alpha)$ is centered
at 64.55$^\circ$ with a rather small deviation of only $\pm 0.03^\circ$, for
the whole range of $\alpha$. This result means that for $\hbar\omega=0.084$ eV
and for all values of $\alpha$, the electrons, with the chosen spin pointing
along $z$, will move at the angle of $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)
\sim 64.5^{\circ}$ with respect to the $x$ direction, with the range of  high
speeds $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ shown in the figure.
Also, from Eq. \eqref{eq:gamma-par} we find that
$\gamma^\parallel_{\sigma^\mathrm{z}} (\omega,\alpha)=\alpha = 64.56^\circ$,
with $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 631.1$\,Km/s 
(as indicated by the green dot-dashed arrow), and that from Eq. \eqref{eq:gamma-perp},
$\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=64.50^\circ$,
gives $\alpha=154.50^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 191.5$ Km/s 
(as indicated by the orange long-dashed 
arrow). 
Thus, at $\hbar\omega=0.084$ eV, an incident field, polarized at
$\alpha \sim 65.5^\circ$ or $\sim 154.5^\circ$, injects electrons with their
spin polarized along $z$, which move parallel or perpendicular to the incident
electric field,  with a speed of 631.14\,Km/s or 191.5\,Km/s, respectively.

Now, we analyze the results for the second energy range of the Up structure
shown in Fig.~\ref{fig:vab-str-comp}. In the top panel
of Fig. \ref{fig:up-vsz-w2}, we plot $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha)$ {\it vs.} 1.950\,eV$\leq\hbar\omega\leq$1.960\,eV and
$0^\circ\leq\alpha\leq 180^\circ$. We see two broad peaks that maximize at
$\alpha=35^{\circ}$ and $\hbar\omega= 1.954$\,eV, with a value of
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 193.5$\,Km/s, and at
$\alpha=35^{\circ}$ and $\hbar\omega= 1.957$\,eV, with a value of
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 170.6$\,Km/s. We only
analyze the highest  maximum in the bottom panel, where we  show
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ (left scale,
black solid line) {\it vs.} $\alpha$, at $\hbar\omega= 1.954$\,eV, thus following the highest ridge
shown in the 3D plot of the top panel. Also, we plot the corresponding velocity
angle $\gamma_{\sigma^\mathrm{z}}(\omega,\alpha)$ (right scale, red short-dashed  line),
where in this case we see that the values of $\gamma_{\sigma^z}(\omega,\alpha)$
have more dispersion, as a function of $\alpha$, than for the lower energy
range shown in the bottom panel of Fig.~\ref{fig:up-vsz-w1}. However,
$\gamma_{\sigma^z}(\omega,\alpha)\sim 77.8^\circ$ is nearly constant from
$\alpha=0^\circ$ up to $\alpha\sim 85^\circ$. In this case, we find that
$\gamma^\parallel_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha=78.0^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 115.0$\,Km/s 
(as indicated by the green dot-dashed arrow), and that from Eq. \eqref{eq:gamma-perp},
$\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=167.8^\circ$,
gives $\alpha=77.8^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 65.6$\,Km/s 
(as indicated by the orange long-dashed  arrow). 
Thus, through the correct choice of $\hbar\omega$ and $\alpha$ we could
inject electrons, in this case with their spin polarized along $z$, which move
parallel or perpendicular to the incident electric field, with sizable speeds.

@@

We proceed to analyze the Alt structure, just as we did with the Up structure,
but in this case, we only choose the lower energy range shown in the left
central panel of Fig.~\ref{fig:vab-str-comp}. In the top panel of Fig. 
\ref{fig:alt-vsz}, we plot $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$
{\it vs.} 0.715\,eV$\leq\hbar\omega\leq$0.725\,eV and $0^\circ\leq\alpha\leq
180^\circ$. We see a broad peak that maximizes at $\alpha=150^{\circ}$ and
$\hbar\omega= 0.720$\,eV, with a value of
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 644.9$\,Km/s. In the bottom
panel, we  show $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ (left scale, black solid line) {\it vs.}
$\alpha$, at $\hbar\omega= 0.720$\,eV, thus following
the highest ridge shown in the 3D plot of the top panel. Also, we plot the
corresponding velocity angle $\gamma_{\sigma^\mathrm{z}} (\omega,\alpha)$
(right scale, red short-dashed  line), where now we see that
$\gamma_{\sigma^z}(\omega,\alpha)$ is centered at $109.2^{\circ}$ having
variations of $\pm 1.0^{\circ}$ for $0^{\circ} \leq
\alpha \leq 180^{\circ}$. In this case, we find that
$\gamma^\parallel_{\sigma^\mathrm{z}} (\omega,\alpha) =
\alpha = 108.8^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)
= 450.05$\,Km/s (as indicated by the  green dot-dashed arrow), 
and that from Eq. \eqref{eq:gamma-perp},
$\gamma^\perp_{\sigma^\mathrm{z}}(\omega,\alpha)=\alpha-90^\circ=110.0^\circ$,
gives $\alpha=20.0^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha) = 60.84$\,Km/s 
(as indicated by the orange long-dashed  arrow). Thus, as for the Up structure,
we could inject electrons with a fixed spin, which moves parallel or
perpendicular to the incident electric field.
% Again, for the cases in which the spin polarization is parallel to the
% surface the maximum values are
% $\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha) = 297.8$ Km/s and
% $\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha) = 606.4$ Km/s,
% corresponding to $\gamma_{\mathrm{x}}(\omega,\alpha) = 116.3^{\circ}$
% $\gamma_{\mathrm{y}}(\omega,\alpha) = 110.1^{\circ}$ and both for
% $\alpha=150^{\circ}$, where the plots are not presented.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\tama]{fig7}
\caption{(color online) For the Up structure we show the velocity
$\mathcal{V}_{\mathrm{a}} (\omega,\alpha)$ (left scale, black solid line), the polar
angle $\theta_{\mathrm{a}} (\omega,\alpha)$ (right scale, red dashed  line), and  the
azimuthal angle $\varphi_{\mathrm{a}} (\omega,\alpha)$, (right scale, blue dot-dashed 
line), {\it vs.} $\hbar\omega$, for $\alpha=35^\circ$, and $\mathrm{a}=x$ or
$\mathrm{a}=y$.}
\label{fig:up-vab-comp-rtp-1}
\end{figure}

@@
